Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-15 chi2012.tex
interaction description

@@

>>>>

\subsubsection{Multipath selection: link-sliding for heterogeneous sets}
When working with instances, users may be interested in a particular aspect of an instance rather than just the instance itself; for example, a user may be interested in the price of a particular product, its rating, manufacturer, and so on.  These are represented as \emph{properties} of the item, listed under the name of the instance.  Selecting any of such properties creates a \emph{path   selection} which dereferences all of the instances in that group that have that property, yielding their corresponding values.  For example, selecting the \emph{manufacturer} property for an instance in a group will cause the manufacturer of that item to appear alongside its label, and will also cause the manufacturers of \emph{all other   instances in that group that have a manufacturer property} to be dereferenced (and displayed) as well.  When such a path selection is applied, the properties displayed are updated to be the set of properties of the \emph{terminating value of the path}, so that such value can be further dereferenced.  For example, once selecting a manufacturer, a user may want to know the product's manufacturer's overall reputation, so might select its ``reputation score'' property, thereby extending the path selection.

Instances that cannot be dereferenced by a particular path selection  are left alone;  a second path selection can be created for such insances, which, like the first path selection, causes all like instances to be dereferenced.  Each group can carry an arbitrary number of path selections, and each path selection can be extended arbitrarily deep by selecting successive properties of values. This achieves the ability to \emph{link slide} in the same way introduced by Parallax \cite{parallax}.

@@

\subsection{Summary of interaction features}
